The pollination trade-off

### 2018-07-01 paper/manuscript.Rmd
Explicit namespace in manuscript

consistency <- inner_join(sgg, sgs, by = 'recipient') %>% 
  mutate_at(.vars = c('p.value.x', 'p.value.y'), 
            .funs = function(x) x < 0.05) %>%
  mutate(consistent = p.value.x == p.value.y) %>%
  group_by(recipient) %>%
  summarise(p.value.x = mean(p.value.x), 
            consistent = all(consistent),
            n_sites = n_distinct(site_name)) %>% 
  filter(n_sites > 1)
prop_consistency <- sum(consistency$consistent)/
  nrow(consistency)
```

>>>>

consistency <- dplyr::inner_join(sgg, sgs, by = 'recipient') %>% 
  mutate_at(.vars = c('p.value.x', 'p.value.y'), 
            .funs = function(x) x < 0.05) %>%
  dplyr::mutate(consistent = p.value.x == p.value.y) %>%
  dplyr::group_by(recipient) %>%
  dplyr::summarise(p.value.x = mean(p.value.x), 
            consistent = all(consistent),
            n_sites = dplyr::n_distinct(site_name)) %>% 
  dplyr::filter(n_sites > 1)
prop_consistency <- sum(consistency$consistent)/
  nrow(consistency)
```
